Parameter Space Representation of Pareto Front to Explore Hardware-Software Dependencies

### 2014-05-16 experiments.tex
added pics

Next, a set of the most impacting code compilation parameters has been
selected and included in the configuration space:
\begin{itemize}
\item{tcc\_region}: Specifies the scope of action of the compiler and the type
of code transformation involved (basic block, super block and hyper
block) 
\item {max\_unroll\_allowed}: The number of unroll iterations allowed
\item{regroup\_only}: Avoids inlining 
\item{do\_classic\_opti}: A set of classical optimization, not VLIW related,
such as common expression removal 
\item{do\_prepass\_scalar\_scheduling}: Performs a schedule before
forming regions 
\item{do\_postpass\_scalar\_scheduling}: Performs a schedule after the region formation 
do\_modulo\_scheduling & Modular scheduling 
\item{memvr\_profiled}: Performs a memory-dependencies profiling 
\end{itemize}

@@

The results presented in the next section compare PS against a widely
adpted Multi-objective Genetic Algorithm~\cite{}. At best of our
knowledge, genetic approaches
still represent the best compromise between efficiency (i.e. time
required for exploration) and accuracy of the reported Paret Sets. Of
course, mono-objective approaches have been
deliberately excluded from this analysis. Other
approaches~\cite{dep} that make use of some a-priori knowledge about the
role and meaning of each parameter have been also excluded, since our
aim is evaluate the capacity of focusing on interesting
parameter regions without any external judgement or help based on
euristics.  Finally, it should be pointed
out that in this introductory work we will explicitly use the TODO
variant of MOGA, remainding to works like~\cite{} for a detailed
analysis on how it differs and what could be expected from similar multi-objective strategies.

@@

Figures~\ref{fig:pareto_fronts_100} and~\ref{fig:pareto_fronts}
respectively show the visited configurations and the
Pareto fronts found for both FCP and VCP scenarios for different
application benchmarks. How it can be observed, VCP solutions
are on average  more widely and evenly distributed over the objective
space as compared to those found for the FCP case.

\begin{figure}
  \centering
  \begin{tabular}{cc}
    \includegraphics[width=0.45\textwidth]{pictures/100bmm.eps} & \includegraphics[width=0.45\textwidth]{pictures/100fir_int.eps} \\
    \includegraphics[width=0.45\textwidth]{pictures/100mm.eps} & \includegraphics[width=0.45\textwidth]{pictures/100fib.eps} \\
    \includegraphics[width=0.45\textwidth]{pictures/100alloca_test.eps} & \includegraphics[width=0.45\textwidth]{pictures/100wave.eps}
  \end{tabular}
  \caption{Pareto fronts found by PS and GA for a fixed budget of 100 configurations.}
  \label{fig:pareto_fronts_100}
\end{figure}

\begin{figure}
  \centering
  \begin{tabular}{cc}
    \includegraphics[width=0.45\textwidth]{pictures/bmm.eps} & \includegraphics[width=0.45\textwidth]{pictures/fir_int.eps} \\
    \includegraphics[width=0.45\textwidth]{pictures/mm.eps} & \includegraphics[width=0.45\textwidth]{pictures/fib.eps} \\
    \includegraphics[width=0.45\textwidth]{pictures/alloca_test.eps} & \includegraphics[width=0.45\textwidth]{pictures/wave.eps}
  \end{tabular}
  \caption{Pareto fronts found by PS and GA for a fixed budget of 500 configurations.}
  \label{fig:pareto_fronts}
\end{figure}

>>>>

Next, a set of the most impacting code compilation parameters has been
selected and included in the configuration space:
\begin{itemize}
\item{tcc\_region}: Specifies the scope of action of the compiler and the type
of code transformation involved (basic block, super block and hyper
block) 
\item {max\_unroll\_allowed}: The number of unroll iterations allowed
\item{regroup\_only}: Avoids inlining 
\item{do\_classic\_opti}: A set of classical optimization, not VLIW related,
such as common expression removal 
\item{do\_prepass\_scalar\_scheduling}: Performs a schedule before
forming regions 
\item{do\_postpass\_scalar\_scheduling}: Performs a schedule after the region formation 
do\_modulo\_scheduling  Modular scheduling 
\item{memvr\_profiled}: Performs a memory-dependencies profiling 
\end{itemize}

@@

The results presented in the next section compare PS against a widely
adpted Multi-objective Genetic Algorithm~\cite{}. At best of our
knowledge, genetic approaches
still represent the best compromise between efficiency (i.e. time
required for exploration) and accuracy of the reported Paret Sets.
Note that for the reasons described above, mono-objective approaches have been
explicitly excluded from this analysis. Same decision has been taken
for other approaches (e.g. dependecy based~\cite{dep}) that make use of some a-priori knowledge about the
role and meaning of each parameter, since our
aim is evaluate the capacity of focusing on interesting
parameter regions without any external judgement or help based on
euristics.  Finally, it should be pointed
out that in this introductory work we will explicitly use the TODO
variant of MOGA, remainding to works like~\cite{} for a detailed
analysis on how it differs and what could be expected from similar multi-objective strategies.

@@

\begin{table*}
  \centering
  \begin{tabular}{ccc}
    \includegraphics[width=0.32\textwidth]{pictures/alloca_100.eps} &
    \includegraphics[width=0.32\textwidth]{pictures/bmm_100.eps} & 
    \includegraphics[width=0.32\textwidth]{pictures/fir_int100.eps} \\
    \includegraphics[width=0.32\textwidth]{pictures/mm_100.eps} &
    \includegraphics[width=0.32\textwidth]{pictures/sha_100.eps} &
    \includegraphics[width=0.32\textwidth]{pictures/wave_100.eps} 
  \end{tabular}
  \caption{Pareto fronts found by PS and GA for a fixed budget of 100 configurations.}
  \label{fig:pareto_fronts_100}
\end{table*}

\begin{table*}
  \centering
  \begin{tabular}{ccc}
    \includegraphics[width=0.32\textwidth]{pictures/alloca_500.eps} &
    \includegraphics[width=0.32\textwidth]{pictures/bmm_500.eps} & 
    \includegraphics[width=0.32\textwidth]{pictures/fir_int500.eps} \\
    \includegraphics[width=0.32\textwidth]{pictures/mm_500.eps} &
    \includegraphics[width=0.32\textwidth]{pictures/sha_500.eps} &
    \includegraphics[width=0.32\textwidth]{pictures/wave_500.eps} 
  \end{tabular}
  \caption{Pareto fronts found by PS and GA for a fixed budget of 500 configurations.}
  \label{fig:pareto_fronts_100}
\end{table*}
Figures~\ref{fig:pareto_fronts_100} and~\ref{fig:pareto_fronts}
respectively show the visited configurations and the
Pareto fronts found for both FCP and VCP scenarios for different
application benchmarks. How it can be observed, VCP solutions
are on average  more widely and evenly distributed over the objective
space as compared to those found for the FCP case.
